% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Rohan Chandra}
\newcommand{\CVTitle}{Rohan Chandra's CV}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{https://rohanchandra30.github.io/}

% PDF settings and properties.
% \hypersetup{
% pdftitle={\CVTitle},
% pdfauthor={\CVAuthor},
% pdfsubject={\CVWebpage},
% pdfcreator={XeLaTeX},
% pdfproducer={},
% pdfkeywords={},
% unicode=true,
% bookmarks=true,
% bookmarksopen=true,
% pdfstartview=FitH,
% pdfpagelayout=OneColumn,
% pdfpagemode=UseOutlines,
% hidelinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
{9210 Rhode Island Avenue, College Park, MD, 20740}
\par
{rohan@cs.umd.edu}
\,\SubBulletSymbol\,
+1\,(240)\,447-5891
\,\SubBulletSymbol\,
\CVWebpage
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
{\textbf{University of Maryland}},
College Park, MD, USA

\Gap
\BulletItem
M.S. in
{Computer Science}
\hfill
\DatestampYMD{2016}{08}{15} --
\DatestampYMD{2018}{05}{15}
\begin{Detail}
\SubBulletItem
Cumulative GPA: 3.837 / 4.000
\SubBulletItem
Relevant Courses: Optimization, Machine Learning, Liner Algebra, Probability and Statistics.
\end{Detail}

\BigGap
\Entry
{\textbf{Delhi Technological University}},
New Delhi, India

\Gap
\BulletItem
B.Tech. in
{ECE}
\hfill
\DatestampYMD{2012}{08}{15} --
\DatestampYMD{2016}{05}{15}
% \begin{Detail}
% \SubBulletItem
% Last 2 years GPA: 80.00 / 100.00
% \end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\Entry
{\textbf{{University of Maryland}},
College Park, MD, USA

\Gap
\BulletItem
Graduate Research Assistant, Computer Science Dept
\hfill
\DatestampYMD{2017}{04}{15} -- Present
% \DatestampYMD{2005}{05}{15}
\begin{Detail}
\SubBulletItem
\textbf{Developed Phasepack: }Phase Retrieval is an example of a non-convex quadratic program with
quadratic constraints. In the real-valued case, it is a combinatorial problem which is known to be NP-hard. Despite
this observation, recent years have seen the development of new algorithms that solve phase retrieval problems ef-
fectively. Unfortunately, because of the lack of publicly available real-world data, the lack of a common software
interface for different algorithms, and a knowledge gap between practitioners and theoreticians, only little work has
been devoted to compare and evaluate newer phase retrieval methods. So we created Phasepack, comprehensive library that compiles all the algorithms within a uniform interface.

\SubBulletItem
\textbf{Low Rank Matrix Recovery: }Another example of intractability associated with non-convexity is low rank matrix recovery with quadratic measurement constraints where a solution is
obtained by lifting the problem to a higher parameter space. To elaborate, lifting expresses a system of quadratic
measurements as a system of linear equations whose solution is a matrix that obeys a rank constraint. However,
working with matrices instead of vectors in higher dimensions generally means incurring large storage costs. As
part of my MS thesis I am trying to solve the problem of low rank matrix recovery from quadratic measurement
constraints without lifting i.e. in the natural parameter space. We observed that that Phasemax (Goldstein and Studor, 2016) solves phase retrieval by recovering solutions in the same space as the input without lifting to higher
dimensions. Consequently it is a better alternative to current lifting solutions for solving SDP’s. Initial sketches of
my proof look promising and I am currently in the process of formalizing this.
\end{Detail}


%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work Experience}
{Work Experience}
{PDF:ResearchExperience}

\Entry
{\textbf{{IIIT Delhi}},
New Delhi, India

\Gap
\BulletItem
Intern, Swarath - The Driverless Car Project
\hfill
\DatestampYMD{2016}{01}{15} --
\DatestampYMD{2016}{06}{15}
\begin{Detail}
\SubBulletItem
Helped design the lane detection module for the perception module using ROS, C++, and OpenCV.

\SubBulletItem
Implemented the localization and navigation algorithms used in the planning module.

\SubBulletItem
Helped design India's first joystick enabled e-Rickshaw. Won the \textbf{first prize} in IIIT Delhi's Research Showcase in March 2016
\end{Detail}

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

\SubSection
{Journals}
{Journals}
{PDF:Journals}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\Gap
\NumberedItem{[1]}
\href{http://www.jstor.org/stable/10.4169/college.math.j.47.4.281}
{Arthur Benjamin, \underline{Rohan Chandra},
``Multiplying by 9,''
\textit{The College Mathematics Journal},
vol.47,
no.~4,
pp.~281,
\DatestampYM{2016}{09}.}

\Gap
\NumberedItem{[2]}
\href{https://search.proquest.com/openview/324892b65f61b2bd4cee1526c67b0ef8/1?pq-origsite=gscholar&cbl=2030624}
{Rashika Anurag, Neeta Pandey, \underline{Rohan Chandra}, Rajeshwari Pandey,
``Voltage Mode Second Order Notch/All - Pass Filter Realization Using OTRA,''
\textit{i-Manager's Journal on Electronics Engineering},
vol.~6,
no.~2,
pp.~22--28,
\DatestampYM{2015}{12}.}

\endgroup

\BigGap
\SubSection
{Conferences}
{Conferences}
{PDF:Conferences}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[8888]}

\Gap
\NumberedItem{[3]}
\href{https://arxiv.org/abs/1712.08838}
{\underline{Rohan Chandra}, S Grover, K Lee, M Meshry, A Taha, ``Texture Synthesis with Recurrent Variational Auto-Encoder,'' in \textit{arXiv Preprint},
\DatestampYM{2017}{12}.}

\Gap
\NumberedItem{[4]}
\href{https://arxiv.org/abs/1711.10175}
{\underline{Rohan Chandra}, Ziyuan Zhong, Justin Hontz, Val McCulloch, Christoph Studer, Tom Goldstein,
``Phasepack: A Phase Retrieval Library,''
 submitted to \textit{IEEE Proceedings of the 51st Asilomar Conference on Signals, Systems and Computers},
Asilomar, CA, USA,
\DatestampYM{2017}{11}.}

\Gap
\NumberedItem{[5]}
\href{https://arxiv.org/abs/1711.09777}
{\underline{Rohan Chandra}, Ziyuan Zhong, Justin Hontz, Val McCulloch, Christoph Studer, Tom Goldstein,
``Phasepack User Guide,''
in \textit{arXiv Preprint},
\DatestampYM{2017}{11}.}


\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Achievements \& Strengths}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
Top Writer on Quora in mathematical optimization category
\hfill
% \DatestampY{2017}
% \DatestampY{2005}


\Gap
\BulletItem
State level chess player

\Gap
\BulletItem
Speed math
\begin{Detail}
\Item
Published a number of techniques for speed arithmetic without paper and pencil.
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Service}
{Professional Affiliations \& Activities}
{PDF:ProfessionalAffiliationsActivities}

\Entry
{Dept of computer science, UMD},
\newline
College Park, MD, USA

\Gap
\BulletItem
Application Reviewer for graduate school admissions.
\hfill
\DatestampY{2016} --
Present

% Manual page break.
% \newpage


% %%%%%%%%%%%%%%%
% %% LANGUAGES %%
% %%%%%%%%%%%%%%%

% \Section
% {Languages}
% {Languages}
% {PDF:Languages}

% \BulletItem
% Hindi: Native language.

% \Gap
% \BulletItem
% English: Fluent (speaking, reading, writing).

% \Gap
% \BulletItem
% German: Fluent (reading, writing); intermediate (speaking).

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Technical Skills}
{Skills}
{PDF:Skills}

\Entry
Python,
MATLAB,
{\LaTeX},
Microsoft Office Suite

\BigGap


%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests}
{Interests}
{PDF:Interests}

\Entry
Chess,
Academia,
Mental Math,

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

% \Section
% {References}
% {References}
% {PDF:References}

% \BulletItem
% \textbf{Dr. Tom Goldstein}
% \newline
% Assistant Professor of Computer Science
% \newline
% University of Maryland,
% \newline
% College Park, MD, USA
% \newline
% \href{mailto:tomg@cs.umd.edu}
% {tomg@cs.umd.edu}
% \,\SubBulletSymbol\,
% +1\,(301)\,405-0053

% \BigGap
% \BulletItem
% \textbf{Jason Filippou}
% \newline
% Lecturer of Computer Science
% \newline
% University of Maryland,
% \newline
% College Park, MD, USA
% \newline
% \href{mailto:jasonfil@umiacs.umd.edu}
% {jasonfil@umiacs.umd.edu}
% \,\SubBulletSymbol\,
% +1\,(301)\,405-2726


% \BigGap
% \BulletItem
% \textbf{Dr. Yiannis Aloimonos}
% \newline
% Professor of Computer Science
% \newline
% University of Maryland,
% \newline
% College Park, MD, USA
% \newline
% \href{mailto:yiannis@cs.umd.edu}
% {yiannis@cs.umd.edu}
% \,\SubBulletSymbol\,
% +1\,(301)\,405-1743


\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

% \UseNoteFont%
% \null\hfill%
% [\textit{\CVNote}]

\end{document}
